Global phase diagram and possible quantum spin liquid in the triangular $J$-$K$-$\Gamma$ model

### 2020-07-29 paper/paper.tex
20200729 9:25

\documentclass[aps,prb,reprint,amsfonts,amsmath,amssymb,showpacs,groupedaddress,superscriptaddress]{revtex4-1}
\usepackage{IEEEtrantools}
\usepackage{graphicx}
\usepackage{bm}
\usepackage{color}
% \usepackage{changes}
    % \definechangesauthor[name={Wang Shi}, color=orange]{swang}

\usepackage[colorlinks,urlcolor=blue,linkcolor=blue,anchorcolor=blue,citecolor=blue,bookmarks]{hyperref}

@@

\title{Global phase diagram and possible quantum spin liquid in the triangular $J-K-\Gamma$ model}

@@

\begin{abstract}
The global ground state phase diagram of the Heisenberg-Kitaev-$\Gamma$ model on a triangular lattice is studied using classical Monte Carlo and exact diagonalization. The quantum phase diagram is quite similar to the classical case except for a small area of possible QSL near the $\Gamma=1$ point. The continuum in the spin excitation spectrum and no spectrum intensity at zero energy indicates that the ground state of the model in this area is gapped QSL. As for the exotic phase near the antiferromagetic Kitaev point, our exact diagnoalization results provide evidence that it is stripe phase and the ordered moment along the cubic axes direction. In adition to the identification of these novel phases, we made a detailed distinction between these FM and stripe phases which occupy the majority area of the global phase diagram.
\end{abstract}

@@

\section{\label{sec:SectionI}Introduction}
Geometric frustration, which arises when the lattice geometry gives rise to constraints that cannot be simultaneously satisfied, plays an important role in various kinds of magnetic systems. In particluar, antiferromagnets on the triangular lattice are typical examples of such geometric frustated spin systems and have attracted numerous interests in condensed matter physics. For nearest-neighbor (NN) spin-1/2 antiferromagetic Heisenberg model on triangular lattice, though a fully disordered resonating-valence-bond (RVB) \cite{Anderson1973} state was proposed as the possible ground state in the early years, several studies point to a 120$^\circ$ N\'{e}el-ordered ground state thereafter \cite{PhysRevLett.99.127004,PhysRevLett.82.3899,PhysRevB.50.10048,PhysRevLett.60.2531}. When the second NN interactions are included which introduce further frustration, the system has a much richer phase diagram including the 120$^\circ$ N\'{e}el state, the stripe state and a spin liquid state \cite{PhysRevB.91.014426,PhysRevB.92.041105,PhysRevB.92.140403,PhysRevB.96.165141,PhysRevB.93.144411,JPSJ.83.093707,PhysRevB.96.075116,PhysRevB.94.121111,PhysRevLett.123.207203}. All these studies have revealed that geometric frustated systems show quite different behavior from that of the non-frustated system.

On the other hand, exchange frustation in systems with strongly anisotropic magnetic interactions has been shown to be another promising approach to explore exotic quantum spin states. Like geometric frustation, the effect of exchange frustration is to prevent the formation of long range magnetic order and give raise to a residual ground-state entropy. The spin-1/2 Kitaev model \cite{Kitaev2006} on honeycomb lattice, which has both gapped and gapless quantum spin liquid (QSL) ground state (GS) supporting fractionalized excitations, is an example of a model with exchange frustration. Because of its theoretical importance and potential application in quantum computing, great efforts have been made to search for a solid-state realization of the Kitaev model. Khaliullin \emph{et al.,} \cite{Khaliullin2005, PhysRevLett.102.017205} proposed to realized this highly anisotropic spin model in 4d/5d systems with a low spin state of $d^5$ configuration, such as iridates $A_2$IrO$_3$ (A = Na, Li). In these systems, the bond-directional interactions originate from the joint effects of strong spin-orbit coupling (SOC), electron interactions, $d^5$ configuration and 90$^\circ$ bond geometry formed by edge sharing octahedra. The resulting Hamiltonian is the Heisenberg-Kitaev (HK) model. It was later extended to contains more terms such as the off-diagonal $\Gamma$ term \cite{PhysRevLett.112.077204}. In fact, magnetic ions located at the center of edge-shared octahedra can not only form honeycomb lattice, but also triangular lattice (see Fig.~\ref{fig:ModelDefinition}(a)) and the Kitaev term can naturally be generalized to this scenario \cite{PhysRevB.93.104417,PhysRevB.89.014414}. Moreover, the symmetric off-diagonal $\Gamma$ term is allowed by symmetry and is a generic feature of S=1/2 models with edge sharing octahedra \cite {PhysRevLett.112.077204}. Kai Li \emph{et al.,} \cite{KaiLi2015} have studied the HK model on triangular lattice and a global phase diagram with a mean-field level chiral spin liquid (SL) as well as four magnetically ordered phases has been obtained. However, the effect of the $\Gamma$ term on triangluar lattice has not gain as much attention as on honeycomb lattice \cite{PhysRevLett.112.077204,Rau2014,PhysRevLett.118.107203,PhysRevB.96.115103,PhysRevB.93.214431,PhysRevB.100.144422}.

On the experimental side, the discovery of YbMgGaO$_4$ has invoked increasing interest in searching for rare-earth based spin-frustrated materials \cite{srep16419,PhysRevLett.115.167203,PhysRevB.94.035107,PhysRevB.96.054445,PhysRevB.97.184413,PhysRevB.97.125105,PhysRevB.96.075105,PhysRevLett.119.157201}. The Yb$^{3+}$ ions form a triangular layer and are surrounded by O$^{2-}$ which construct edge sharing octahedra \cite{srep16419,PhysRevLett.115.167203}. More recently, a class of compounds AReCh$_2$ (A=alkali, Re=rare-earth, Ch=O, S, Se) with perfect triangular lattices of rare-earth ions have been synthesized and explored. The magnetic susceptibilty and heat capacity data suggest no long-range magnetic order or spin freezing down to the lowest measurement temperature, which implies their candidacy for QSL state \cite{acsmaterialslett.9b00464,PhysRevMaterials.3.114413,arXiv1911.08036,Liu_2018,PhysRevB.99.180401,PhysRevB.100.224417,PhysRevB.100.144432}. The novel magnetic properties of these triangluar magnets may be attributed to the interplay of geometric frustation and exchange frustration induces by spin-orbit coupling.

Inspired by previous theoretical and experimental works, we study the Heisenberg-Kitaev-$\Gamma$ ($J-K-\Gamma$) model on the triangular lattice. The $J-K-\Gamma$ model Hamiltonian is given by
\begin{equation}
    H=\sum_{\langle i,j \rangle \in \alpha \beta (\gamma)} \lbrack J \bm{S}_i \bm{\cdot} \bm{S}_j + K S_i^{\gamma} S_j^{\gamma} + \Gamma (S_i^{\alpha} S_j^{\beta} + S_i^{\beta} S_j^{\alpha}) \rbrack \label{eq:Hamiltonian}
\end{equation}
where $\langle i,j \rangle$ denotes the NN bonds, $\gamma$ takes value $x$, $y$, or $z$ depending on the direction of the NN bond as shown in Fig.~\ref{fig:ModelDefinition}(c), and $\alpha$, $\beta$ are the remaining directions. $J$ and $K$ are the magnitude of the Heisenberg and Kitaev interactions and $\Gamma$ the symmetric off-diagonal exchanges. To the best of our knowledge, no exact solution has been reported so far for the spin-1/2 Kitaev and/or $\Gamma$ model on the triangular lattice. Therefore, it remains conceptually interesting to investigate whether the QSL could exist as a possible ground state of the triangular $J-K-\Gamma$ model.

\begin{figure}
    \includegraphics[width=\columnwidth]{Fig1.pdf}
    \caption{\label{fig:ModelDefinition}(Color online) (a) Top view of the triangular lattice of the edge-sharing octahedron. (b) The orientation of the cubic $x$, $y$, $z$ axes with respect to the octahedron. The spin operators $S^x$, $S^y$ and $S^z$ are defined with respect to this reference frame. (c) Three types of the NN bonds on the triangular lattice, namely $\gamma=x, y, z$ colored red, green and blue, respectively. The different colors of the lattice sites label the four sublattices realizing the four-sublattice-transformation, see the main text for detailed information.}
\end{figure}

The rest of the paper is organized as follows: The classical Monte Carlo and exact diagnoalization (ED) methods are introduced in Sec.~\ref{sec:SectionII}. Section~\ref{sec:SectionIII} discusses the phases of the classical $J-K-\Gamma$ model with the main focus on the direction of the ordered moment of the FM and stripe states. The global phase diagram of the quantum model is presented in Sec.~\ref{sec:SectionIV} along with a detailed discussion of its phases.

\section{\label{sec:SectionII}Methods}
The full anisotropic Hamiltonian~\eqref{eq:Hamiltonian} is no longer exactly solvable, even for the classical case. One, therefore, either has to rely on approximate analytical method or on numerical techniques. To determine the ground state of the Hamiltonian~\eqref{eq:Hamiltonian}, we employ a combination of classical Monte Cralo simulation and ED calculation. Here, we briefly describe the methods we used. For convenience, we fix the energy scale with $\sqrt{J^2 + K^2 + \Gamma^2}=1$ and parametrize the exchanges using spherical angles $\alpha$ and $\beta$
\begin{equation}
    J = \sin\alpha \sin\beta, \quad
    K = \sin\alpha \cos\beta, \quad
    \Gamma = \cos\alpha \label{eq:Parameters}
\end{equation}
where $\alpha \in [0, \pi]$ and $\beta \in [0, 2\pi]$ to cover the global phase diagram.

\subsection{\label{sec:SectionIIA}Classical Monte Carlo}
\textcolor{red}{A introduction to classical Monte Carlo. To be accomplished $\cdots \cdots$}

\subsection{\label{sec:SectionIIB}Exact Diagonalization}
We perform Lanczos ED calculations of the GS of the Hamiltonian~\eqref{eq:Hamiltonian} on a $4 \times 6$ cluster with periodic boundary conditions (PBC). To detect quantum phase transitions, the second derivatives of the ground state energy, $-\partial^2E_0/\partial\alpha^2$ and $-\partial^2E_0/\partial\beta^2$ were computed and looked for singular features that indicate changes in the ground state characteristics. Phases containing exactly solvable or well-understood points, such as the FM, 120$^\circ$ N\'{e}el, stripe and Dual N\'{e}el can be readily identified. To have a better understanding of the characteristics of the remaining phases, we examine the static magnetic structure factor (SMSF) $S(\bm{Q})$ and dynamic spin excitation spectrum $A(\bm{k}, \omega)$ of these phases. $S(\bm{Q})$ and $A(\bm{k}, \omega)$ are defined as follow:
\begin{subequations}
    \begin{align}
        & S(\bm{Q}) = \frac{1}{N} \sum_{ij} \langle \Omega | \bm{S}_i \bm{\cdot} \bm{S}_j | \Omega \rangle e^{i \bm{Q} \bm{\cdot} (\bm{R}_i - \bm{R}_j)} \label{eq:SMSF} \\
        & A(\bm{k}, \omega) = -\frac{1}{\pi} \text{Im} G(\bm{k}, \omega) \label{eq:Akomega} \\
        & G(\bm{k}, \omega) = \frac{1}{N} \sum_{ij} G_{ij}(\omega) e^{i \bm{k} \cdot (\bm{R}_i - \bm{R}_j)} \\
        & G_{ij}(\omega) = \langle \Omega | S_i^{+} \frac{1}{\omega + i\eta - H + E_0} S_j^{-} | \Omega \rangle \label{eq:GreenFunction}
    \end{align}
\end{subequations}
where $| \Omega \rangle$ and $E_0$ are the GS and ground state energy respectively, N is the total number of spins, $\bm{R}_i$ the position of site $i$, and $\eta = 0^+$.

To extract the moment direction of a magnetic ordered phase from a cluster GS, we employ the method developed by Ji\v{r}\'{i} Chaloupka \emph{et  al} \cite{PhysRevB.94.064435}. The basic idea of this method is to measure the probabilities of the exact cluster GS on cluster spin-coherent states with varying moment directions. The cluster spin-coherent state is a direct product of spin-1/2 coherent states on each site $i$
\begin{equation}
    | \Psi \rangle = \bigotimes_{i=1}^N | \theta_i, \phi_i \rangle \label{eq:ClusterCoherentState}
\end{equation}
where the spin-1/2 coherent state
\begin{equation}
    | \theta, \phi \rangle = \mathcal{R}_z(\phi) \mathcal{R}_y(\theta) | \uparrow \rangle = e^{-i \phi S^z} e^{-i \theta S^y} | \uparrow \rangle \label{eq:Spin-1/2CoherentState}
\end{equation}
is fully polaried along the $(\theta, \phi)$ direction. Here the cubic axes are used (see Fig.~\ref{fig:ModelDefinition}(b)), $\theta$ and $\phi$ are the conventional spherical angles, and $S^z | \uparrow \rangle = \frac{1}{2} | \uparrow \rangle$. By calculating the overlap between the exact cluster GS and cluster spin-conherent states, and maximizing the probability $P = | \langle \Psi | GS \rangle|^2$ with respect to $\theta$s and $\phi$s, we can then identify the classical pattern that best fits the exact GS.

\section{\label{sec:SectionIII}Classical Analysis}
To understand the effects of inculding the off-diagonal $\Gamma$ term, we first study the classical $J-K-\Gamma$ model where the spin operators are viewed as unit-vectors in three dimension. On our proceeding, we note that the global phase diagram has been obtained previously by using a combination of Luttinger-Tsiza (LT) and classical Monte Carlo simulations \cite{PhysRevB.92.165108}. Six different magnetic orderings: ferromagnet (FM), stripe, 120$^\circ$ N\'{e}el order, nematic, $\mathbb{Z}_2$ and dual-$\mathbb{Z}_2$ vortex crystal phases were found, see Fig.~2 in Ref~\onlinecite{PhysRevB.92.165108}. Our classical Monte Carlo study give qualitatively the same phase diagram.

\subsection{\label{sec:SectionIIIA}Moment direction of the classcial FM order}
For classical FM states, all spins are aligned in parallel and the energy of the $J-K-\Gamma$ model per lattice site is given by
\begin{equation}
    E_{FM}^{c} = (3J + K) + 2 \Gamma (v^x v^y + v^y v^z + v^z v^x) \label{eq:EcFM}
\end{equation}
where $v^x$, $v^y$, $v^z$ are the corresponding components of the classical moment vector. On this level, the moment direction of the classical FM state is determined solely by $\Gamma$ and the problem becomes finding the global minimum and maximum of the multi-variable function $f(v^x, v^y, v^z) = v^x v^y + v^y v^z + v^z v^x$ with the constraint $|\bm{v}| = 1$. $f(v^x, v^y, v^z)$ takes maximum value $f_{max}=1$ at $v^x=v^y=v^z=\pm 1/\sqrt{3}$ and minimum value $f_{min}=-0.5$ when the conditions $v^x + v^y + v^z = 0$ and $|\bm{v}| = 1$ are fulfilled. The condition $v^x + v^y + v^z = 0$ specifies a plane that passes the coordinate origin and is perpendicular to the $[111]$ direction. Considering the reference frame shown in Fig.~\ref{fig:ModelDefinition}(b) this is actually the plane of the triangular lattice. That is to say, for $\Gamma > 0$ the ordered moment of the classcial FM state prefers to lie in the lattice plane and when $\Gamma$ is negative, the ordered moment would perpendicular to the lattice plane.

Our classical Monte Carlo simulation found FM ordered state with the right moment direction for majority of the area marked as FM phase (see Fig.~2 in Ref~\onlinecite{PhysRevB.92.165108}) except for the pure $\Gamma$ term. For pure positive $\Gamma$ interaction, apart from the FM order lie in the lattice plane, we also found disordered states which have the same energy as the FM state but no states with lower energy were found. When $\Gamma=-1$, in addition to the FM order perpendicular to the lattice plane, other long-range ordered states which are energetically degenerate with the FM state appear (see Appendix~\ref{apx:AppendixA} for details). Based on these observation, it is reasonable to say that the GS of the classical $\Gamma$ model is highly degenerate though the degeneracy may be lifted by introducing other interactions. For example, a ferromagnetic ($J<0$) Heisenberg interaction would break the degeneracy and select the FM ordered state as the GS. On the other hand, when positive Heisenberg interaction is included, which introduces further frustation to the system, the FM order is unlikely to be the GS. In fact, the classical GS were found to be disordered for $0 < J \ll \Gamma$ and stripe ordered for $0 < J \ll -\Gamma$. As for the disordered phase, when quantum flucations are involved, a quantum spin liquid state may emerge.

>>>>

\documentclass[aps,prb,reprint,amsfonts,amsmath,amssymb,showpacs,groupedaddress,superscriptaddress]{revtex4-1}
\usepackage{bm}
\usepackage{color}
\usepackage{graphicx}
\usepackage[colorlinks,urlcolor=blue,linkcolor=blue,anchorcolor=blue,citecolor=blue,bookmarks]{hyperref}

@@

\title{Global phase diagram and possible quantum spin liquid in the triangular $J$-$K$-$\Gamma$ model}

@@

\begin{abstract}
The celebrated Kitaev honeycomb model provides an analytically tractable example with an exact quantum spin liquid ground state. While in real materials, other types of interactions besides the Kitaev coupling are present and these models can also be generalized to a triangular lattice. Here, we study the classical and quantum Heisenberg-Kitaev-$\Gamma$ model on a triangular lattice using the classical Monte Carlo and exact diagonalization. We find that the quantum phase diagram is quite similar to its classical counterpart in the large region, suggesting that the Kitaev physics would have emerged largely in the classical limit. Near the antiferromagetic (AF) Kitaev point, we show that the stripe order is selected out of the classic nematic order via the order-by-disorder mechanism. Around the AF $\Gamma$ point, we find a possible quantum spin liquid in a noticeable region with a continuum in spin excitations.
\end{abstract}

@@

\section{\label{sec:Introduction}Introduction}
Geometric frustration, which arises when the lattice geometry gives rise to constraints that not every exchange bond can be simultaneously minimized in energy, plays an important role in various kinds of magnetic systems. The nearest-neighbor (NN) antiferromagetic (AFM) Heisenberg model on the triangular lattice is a typical example, once two of the spins on an elementary triangle are antiparallel to satisfy their antiferromagnetic interaction, the third one can no longer point in a direction opposite to both other spins. In particular, the special case where spins are $S=1/2$ has attracted numerous interests and was extensively studied after the seminal prediction by Anderson of a "quantum spin liquid" (QSL) where a strong quantum fluctuation prevents any long-range order down to the zero temperature~\cite{Anderson1973}, although it has been shown by later studies that the ground state (GS) have a classical magnetic order with each spin on a triangle pointing to 120$^\circ$ with respect to each other~\cite{PhysRevLett.99.127004,PhysRevLett.82.3899,PhysRevB.50.10048,PhysRevLett.60.2531}. When the second NN interactions are included which introduce further frustration, the system has a much richer phase diagram including the 120$^\circ$ N\'{e}el state, the stripe state and a QSL state~\cite{PhysRevB.91.014426,PhysRevB.92.041105,PhysRevB.92.140403,PhysRevB.96.165141,PhysRevB.93.144411,JPSJ.83.093707,PhysRevB.96.075116,PhysRevB.94.121111,PhysRevLett.123.207203}. All these studies have revealed that geometric frustated systems show quite different behavior from that of the non-frustated system.

On the other hand, exchange frustation in systems with strongly anisotropic magnetic interactions has been shown to be another promising approach to explore exotic quantum spin states. Like geometric frustation, the effect of exchange frustration is to prevent the formation of long range magnetic order and give raise to a residual ground-state entropy. The spin-$1/2$ Kitaev model~\cite{Kitaev2006} on honeycomb lattice, which has both gapped and gapless QSL states supporting fractionalized excitations, is a celebrated example of a model with exchange frustration. In this model, the spins subject to the Kitaev interactions consisting of nearest neighbor Ising-type interactions, with the quantization axis depending on the spatial orientation of an exchange bond. Because of its theoretical importance and potential application in quantum computing, great efforts have been made to search for a solid-state realization of the Kitaev model. G. Khaliullin \emph{et al.,}~\cite{Khaliullin2005,PhysRevLett.102.017205} proposed that this highly anisotropic Kitaev interaction can be realized in 4d/5d systems with a low spin state of $d^5$ configuration, such as iridates A$_2$IrO$_3$ (A = Na, Li). In these systems, the bond-directional interactions originate from the joint effects of strong spin-orbit coupling (SOC), electron interactions, $d^5$ configuration and 90$^\circ$ bond geometry formed by edge sharing octahedra. However, in real materials, other types of interaction besides the Kitaev coupling are present, and these interactions may induce other interesting ordered and disordered phases. The simplest extension of the pure Kitaev model is the Heisenberg-Kitaev (HK) model~\cite{PhysRevLett.105.027204}, in which the NN Heisenberg interaction is also taken into account. This model has been extensively studied by various numerical methods~\cite{PhysRevLett.110.097204,PhysRevB.83.245104,PhysRevB.84.100406,PhysRevB.90.195102,PhysRevLett.119.157203}, which reveal the presence of four magnetically ordered phases with collinear spin patterns of ferromagnetic (FM), AFM, stripy, and zigzag types, besides extended spin-liquid phases near the Kitaev limits. Considering the most idealized crystal structure, another interaction beyond the HK model also must be included, i.e. bond dependent symmetric off-diagonal exchange, which is called the $\Gamma$ interaction~\cite{PhysRevLett.112.077204,PhysRevB.93.214431,PhysRevB.96.115103}. Thus, the generic NN exchange Hamiltonian for the undistorted hexagonal compounds is the $J$-$K$-$\Gamma$ model, where the Heisenberg ($J$), Kitaev ($K$) and $\Gamma$ interactions are all included. Finite $\Gamma$ further enriches the phase diagram by adding non-collinear and incommensurate spiral phases~\cite{PhysRevLett.112.077204}. Moreover, in real materials, such as A$_2$IrO$_3$ and $\alpha$-RuCl$_{3}$, the dominant interactions are the $\Gamma$ and FM Kitaev terms which originate from both direct $d$-$d$ and anion mediated $d$-$p$ electron transfer, while the Heisenberg term has the smallest strength since it predominantly originates from the weak direct $d$-$d$ electron transfer~\cite{PhysRevLett.112.077204,PhysRevB.93.214431,PhysRevB.96.115103}.

In fact, magnetic ions located at the center of edge-shared octahedra can not only form the honeycomb lattice but also the triangular lattice (see Fig.~\ref{fig:ModelDefinition}(a)), so the Kitaev and $\Gamma$ terms can naturally be generalized to the triangular lattice~\cite{PhysRevB.89.014414,PhysRevB.93.104417}. The HK model ($\Gamma=0$) on the triangular lattice has been studied by means of Luttinger-Tisza minimization together with classical Monte Carlo simulation~\cite{PhysRevB.93.104417}, exact diagonalization~\cite{KaiLi2015}, and density matrix renormalization group~\cite{JPSJ.85.114710,PhysRevX.9.021017}. All these methods give consistent results about four magnetically ordered phases: two collinear patterns of FM and stripy types, and two noncollinear patterns of 120$^\circ$ N\'{e}el and noncoplanar spiral types. Note that the distortions of the 120$^\circ$ N\'{e}el order, when the model deviates from the AFM Heisenberg limit ($K=0$, $J>0$), were also called the $Z_{2}$ vortex crystal~\cite{PhysRevB.93.104417,JPSJ.85.114710}. However, the nature of the phase around the antiferromagnetic Kitaev point is still under debate. The Luttinger-Tisza minimization method suggested it to be a $Z_{2}$ vortex crystal~\cite{PhysRevB.93.104417}, the Schwinger-fermion mean-field theory proposed it to be a QSL~\cite{KaiLi2015}, while the density matrix renormalization group calculations suggested it to be a nematic phase~\cite{JPSJ.85.114710} or a stripe phase~\cite{PhysRevX.9.021017}. When the symmetric off-diagonal exchange interaction $\Gamma$ is included, a classical analysis reveals that the stripe and ferromagnetic phases dominate the $J$-$K$-$\Gamma$ phase diagram, in addition to small regions of 120$^\circ$, $Z_{2}$ vortex crystal and nematic phases~\cite{PhysRevB.92.165108}. However, the studies on the effects of quantum fluctuations on the global $J$-$K$-$\Gamma$ phase diagram are scarce. In particular, since no exact solution has been reported so far for the pure spin-$1/2$ Kitaev and $\Gamma$ models on the triangular lattice, it also remains conceptually interesting to investigate whether QSL states could exist as possible GSs due to quantum fluctuations introduced by these exchange-frustrated interactions.

\begin{figure}
    \centering
    \begin{minipage}{0.6\columnwidth}
        \includegraphics[width=\linewidth]{fig/EdgeSharingOctahedrons.pdf}
    \end{minipage}\hspace{0pt}
    \begin{minipage}{0.3\columnwidth}
        \includegraphics[width=\linewidth]{fig/SingleOctahedron.pdf}\vspace{0pt}
        \includegraphics[width=\linewidth]{fig/ModelDefinition.pdf}
    \end{minipage}
    \caption{\label{fig:ModelDefinition}(Color online) (a) Top view of the triangular lattice of the edge-sharing octahedron. (b) The orientation of the cubic $x$, $y$, $z$ axes with respect to the octahedron. The spin operators $S^x$, $S^y$ and $S^z$ are defined with respect to this reference frame. (c) Three types of the NN bonds on the triangular lattice, namely $\gamma=x, y, z$ colored red, green and blue, respectively. The different colors of the lattice sites label the four sublattices realizing the four-sublattice-transformation, see the main text for detailed information.}
\end{figure}

On the experimental side, studies of several classes of rare-earth compounds have recently shown that the quantum spin model on the triangular lattice can be formed by $4f$ moments. In particular, due to their possible Kramers doublets and spin-orbital coupling, the $4f$ electrons can be treated as $S_{eff}=1/2$ at low temperatures, and the spin-orbit entanglement can induce direction-dependent exchanges, such as the $K$ and $\Gamma$ terms. A typical example is YbMgGaO$_{4}$~\cite{srep16419,PhysRevLett.115.167203,PhysRevLett.117.097201,nphys3971,Nature20614,PhysRevLett.117.267202,PhysRevLett.120.087201,PhysRevLett.122.137201,LiAdroja-398}, in which the Yb$^{3+}$ ions form a triangular layer and are surrounded by O$^{2-}$ which construct edge sharing octahedra~\cite{srep16419,PhysRevLett.115.167203}. At low temperatures, QSL states have been proposed due to its lack of long-range magnetic order and the observation of a continuum of magnetic excitations~\cite{srep16419,PhysRevLett.115.167203,PhysRevLett.117.097201,nphys3971,Nature20614}, but the exchange disorder induced by the intermixture of Mg$^{2+}$ and Ga$^{3+}$ may lead to a spin glass state~\cite{PhysRevLett.120.087201} or a random valence bond state~\cite{PhysRevLett.122.137201,LiAdroja-398}. More recently, an alternative family of compounds AReCh$_2$ (A=alkali, Re=rare-earth, Ch=O, S, Se) with perfect triangular lattices of rare-earth ions have been synthesized and explored. The magnetic susceptibilty and heat capacity data suggest no long-range magnetic order or spin freezing down to the lowest measurement temperature, which implies their candidacy for QSL state~\cite{acsmaterialslett.9b00464,PhysRevMaterials.3.114413,arXiv1911.08036,Liu_2018,PhysRevB.99.180401,PhysRevB.100.224417,PhysRevB.100.144432}. These triangluar magnets of rare-earth ions provide suitable platforms to study the interplay of geometric frustation and exchange frustration induced by spin-orbit coupling.

{
    \color{red}The rest of the paper is organized as follows: In Sec.~\ref{sec:Model} we introduce the $J$-$K$-$\Gamma$ model as well as the four-sublattice-transformation that can be applied to the HK model. The exact diagonalization and classical Monte Carlo methods are introduced in Sec.~\ref{sec:Methods}. Section~\ref{sec:Results} disscuss the main results of this paper.
}

\section{\label{sec:Model}Model}

The $J$-$K$-$\Gamma$ model Hamiltonian on the triangular lattice is given by
\begin{equation}
    H = \sum_{\langle i,j \rangle \in \alpha \beta (\gamma)} \lbrack J \bm{S}_i \cdot \bm{S}_j + K S_i^{\gamma} S_j^{\gamma} + \Gamma (S_i^{\alpha} S_j^{\beta} + S_i^{\beta} S_j^{\alpha}) \rbrack,
    \label{eq:Hamiltonian}
\end{equation}
where $\langle i,j \rangle$ denotes the NN bonds, $\gamma$ takes value $x$, $y$, or $z$ depending on the direction of the NN bond as shown in Fig.~\ref{fig:ModelDefinition}(c), and $\alpha$, $\beta$ are the remaining directions. $J$ and $K$ are the magnitude of the Heisenberg and Kitaev interactions, and $\Gamma$ the symmetric off-diagonal exchanges.

In the followings, for convenience, we fix the energy scale with $\sqrt{J^2 + K^2 + \Gamma^2}=1$ and parametrize the exchange interactions using spherical angles $\alpha$ and $\beta$
\begin{equation}
    J = \sin\alpha \sin\beta, \quad
    K = \sin\alpha \cos\beta, \quad
    \Gamma = \cos\alpha
    \label{eq:Parameters}
\end{equation}
where $\alpha \in [0, \pi]$ and $\beta \in [0, 2\pi]$ to cover the global parameter space.

In the HK limit ($\Gamma=0$), the model~\eqref{eq:Hamiltonian} admits an exact duality transformation, i.e., the so-called four-sublattice-transformation (FST)~\cite{PhysRevB.89.014414}. The FST is a spin rotation transformation which divides the triangluar lattice into four sublattices (see Fig.~\ref{fig:ModelDefinition}(c)) and performs the following rotations of the spins on the four sublattices to map the spin $\bm{S}_{i}$ to $\bm{S}_{i}^{\prime}$,
\begin{align*}
    & \bm{S}_{0}^{\prime} = \bm{S}_{0}& \quad \text{for sublattice 0}, \\
    & \bm{S}_{1}^{\prime} = (S_1^x, -S_1^y, -S_1^z)& \quad \text{for sublattice 1}, \\
    & \bm{S}_{2}^{\prime} = (-S_2^x, S_2^y, -S_2^z)& \quad \text{for sublattice 2}, \\
    & \bm{S}_{3}^{\prime} = (-S_3^x, -S_3^y, S_3^z)& \quad \text{for sublattice 3}.
\end{align*}
This corresponds to a $\pi$ rotation around $x$, $y$, and $z$ axis for the sublattices $1$, $2$, and $3$, respectively. The resulting Hamiltonian $H^{\prime}(\bm{S}^{\prime})$ has the same form as the original Hamiltonian albeit with different model parameters $J^{\prime} = -J$ and $K^{\prime} = 2J + K$. For the spherical angles defined in Eq.~\eqref{eq:Parameters}, the mapping takes the form
\begin{align}
    \tan\beta^{\prime} = -\sin\beta / (2\sin\beta + \cos\beta).
    \label{eq:FST}
\end{align}
This special property of the model can help us to identify some exotic magnetically ordered phases from the well established simple counterparts.

\section{\label{sec:Methods}Methods}

\subsection{\label{subsec:MethodED}Exact Diagonalization}

To obtain the quantum phase diagram of the model~\eqref{eq:Hamiltonian}, we perform exact-diagonalization calculations of the GS of the Hamiltonian~\eqref{eq:Hamiltonian} on a $4 \times 6$ cluster with the periodic boundary condition. To detect quantum phase transitions, the second derivatives of the GS energy, $-\partial^2E_0/\partial\alpha^2$ and $-\partial^2E_0/\partial\beta^2$ were computed and its singularities are used to identify possible phase transtions.

To identify the ground-state properties, we first examine the static structure factor (SSF),
\begin{align}
    \mathcal{S}(\bm{Q}) = \frac{1}{N} \sum_{ij} \langle \Omega | \bm{S}_i \cdot \bm{S}_j | \Omega \rangle e^{i \bm{Q} \cdot (\bm{R}_i - \bm{R}_j)},
    \label{eq:SSF}
\end{align}
from which we can find the wave vectors of the ordered phases and distinguish possible QSL states. Here, $|\Omega\rangle$ is the GS, $N$ is the total number of lattice sites, and $\bm{R}_i$ the position of site $i$.

To further determine the magnetic configurations of the magnetically ordered phases, we employ a method by studying the projections of the exact GSs of the finite cluster to the classical states~\cite{PhysRevB.94.064435}. The basic idea of this method is to measure the probabilities of the exact cluster GS on cluster spin-coherent states with varying moment directions. The cluster spin-coherent state is a direct product of spin-1/2 coherent states on each site $i$, i.e.,
\begin{align}
    |\Psi \rangle = \bigotimes_{i=1}^N | \theta_i, \phi_i \rangle,
    \label{eq:ClusterCoherentState}
\end{align}
where the spin-1/2 coherent state
\begin{align}
    |\theta, \phi\rangle = \mathcal{R}_z(\phi) \mathcal{R}_y(\theta) | \uparrow \rangle = e^{-i \phi S^z} e^{-i \theta S^y} | \uparrow \rangle
    \label{eq:Spin-1/2CoherentState}
\end{align}
is fully polaried state along the $(\theta, \phi)$ direction. Here the cubic axes are used (see Fig.~\ref{fig:ModelDefinition}(b)), $\theta$ and $\phi$ are the conventional spherical angles. By calculating the overlap between the exact cluster GS and cluster spin-conherent states, $P = | \langle \Psi | GS \rangle|^2$, and maximizing its value with respect to $\theta$'s and $\phi$'s, we can then identify the classical spin pattern that best fits the exact quantum GS.

Since one of the key characteristics of QSL is the fractional excitation, which can lead to a continuous spectrum, so we study the dynamic structure factor (DSF) $A(\bm{k}, \omega)$ to search for the possible QSLs. $A(\bm{k}, \omega)$ is given by
\begin{align}
    & A(\bm{k}, \omega) = -\frac{1}{\pi} \text{Im} \mathcal{S}(\bm{k}, \omega), \label{eq:Akomega} \\
    & \mathcal{S}(\bm{k}, \omega) = \frac{1}{N} \sum_{ij} \mathcal{S}_{ij}(\omega) e^{i \bm{k} \cdot (\bm{R}_i - \bm{R}_j)}, \\
    & \mathcal{S}_{ij}(\omega) = \langle \Omega | S_i^{+} \frac{1}{\omega + i0^{+} - H + E_0} S_j^{-} | \Omega \rangle, \label{eq:GreenFunction}
\end{align}
where $E_0$ is the ground state energy.

\subsection{\label{subsec:MethodMC}Classical Monte Carlo}

In order to better understand the quantum phases identified by the exact diagonalization method, we also perform classical Monte Carlo simulations. We begin with paralleling-tempering Monte Carlo~\cite{Hukushima96} on 40 replicas with temperature $T/J$ ranging from $0.001$ to $1.0$. For each replica, we sample it with a combination of heat-bath~\cite{Miyatake84} and over-relaxation method~\cite{Berg} mainly on a $24\times 24$ triangle lattice with periodic boundary conditions. A whole MC step consists of a single heat-bath sweep and subsequent 10 over-relaxation sweeps over the entire lattice. We perform $10^6$ MC steps per replica, then, we copy out the spin configuration from the lowest-T replica, and sample it with a combination of zero-temperature heat-bath and over-relaxation method to get the GS. The zero-temperature heat-bath sampling is simply aligning the spins according to their local fields:
\begin{align}
    \bm{S}_i = \frac{\bm{h}_i^{loc}}{|\bm{h}_i^{loc}|} S,
\end{align}
with
\begin{align}
    \bm{h}_i^{loc} = \sum_{\langle j \rangle} J \bm{S}_j + K {S}^{\gamma}_j \hat{e}^{\gamma} + \Gamma (S^\alpha_j \hat{e}^{\beta} + S^\beta_j \hat{e}^\alpha),
\end{align}
For some competing states, we start from several different initial configurations in order to obtain the correct classical GS.

From the magnetic configuration of GS, we compute the spin structure factor given by
\begin{align}
    \mathcal{S}_{\bm{k}} = \frac{1}{N} \sum_{ij} \left \langle \bm{S}_i \cdot \bm{S}_j \right \rangle e^{i \bm{k} \cdot (\bm{r}_i-\bm{r}_j)},
\end{align}
which is a key characterizes to identify magnetic phases.

\section{\label{sec:Results}Results}

\subsection{\label{subsec:GlobalPhaseDiagram}Global Phase Diagram}
